BACI of biomass change for VOCC source cells

### 2019-08-21 analysis/VOCC/4-vocc-BACI.Rmd
exploring match function

#### Set vector type
```{r echo=TRUE}
# climate <- "temperature"
 climate <- "do"
# climate <- "do and temperature"
```

@@

#browser()
  alldata <- rbind(source_biomass, control_biomass) 
  #alldata <- mutate(alldata, treat = ifelse(cell_type=="source", 1, 0))
  #fit <- McSpatial::matchprop(cell_type ~ start_density + depth, data= alldata, ytreat = "source")
  fit_formula <- paste0("cell_type ~ start_density + depth") 
 # fit_formula <- paste0("cell_type ~ start_density + depth + trawled + muddy + any_rock + omega_s")

@@

  matched <- McSpatial::matchprop(as.formula(fit_formula), data = alldata, ytreat = "source")

  matched_time0 <- matched %>% mutate(after = 0, density = start_density) #%>% dplyr::select(-start_density, -end_density)
  matched_time1 <- matched %>% mutate(after = 1, density = end_density) #%>% dplyr::select(-start_density, -end_density)

@@

Prep data
```{r}
data <- vocc_by_sp[["adult"]]
#View(data)

@@

Plot data
```{r}
lapply(variable_names, function(j) {
ggplot(data, aes(y=log_density, x=UQ(rlang::sym(paste(j))), colour=time)) +
  geom_point(alpha=0.35) +
  scale_colour_viridis_d(option="C") 
})

@@

ggplot(data, aes(log_density, fill = cell_type)) +
  geom_histogram(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_wrap(~time)

@@

gam4 <- gamm4::gamm4(as.formula(gamm_formula),random = ~(1|matchobs) + (1|origobs), data=data) # + s(X,Y, bs="re")

@@

plot_parametric(igam4$gam, pred=list(time=c("begin","end"), cell_type=c("control", "source")), 
   parametricOnly = TRUE, main="", xlab ="log_density") 
```

>>>>

#### Set vector type
```{r echo=TRUE}
 climate <- "temperature"
# climate <- "do"
# climate <- "do and temperature"
```

@@

#browser()
  alldata <- rbind(source_biomass, control_biomass) 
  alldata <- mutate(alldata, treat = ifelse(cell_type=="source", 1, 0)) %>% 
    select(-var_2_min, -var_2_max) %>% 
    rename(vect_dist = distance)

  # control_min <- quantile(alldata$start_density[alldata$treat=="0"], 0.05)
  # alldata <- filter(alldata, start_density >= control_min)

  low_biomass <- quantile(alldata$start_density, 0.1)
  alldata <- filter(alldata, start_density >= low_biomass )

  # if (order == "decreasing") 
  #alldata <-   alldata[rev(order(alldata$start_density)), ]
  # 
  # if (order == "increasing") 
  alldata <- alldata[(order(alldata$start_density)), ]

  #browser()

  alldata$depth2 <- alldata$depth^2

  #fit_formula <- paste0("treat ~ start_density") 
  #fit_formula <- paste0("treat ~ start_density + depth") 
  fit_formula <- paste0("treat ~ start_density + depth + trawled + muddy + any_rock + omega_s + x + y")

  # need to be standardized? seems not
  # alldata$start_density.st <- (arm::rescale(alldata$start_density))*10 
  # alldata$depth.st <- arm::rescale(alldata$depth) 
  # alldata$muddy.st <- arm::rescale(alldata$muddy) 
  # alldata$any_rock.st <- arm::rescale(alldata$any_rock) 
  # alldata$omega_s.st <- arm::rescale(alldata$omega_s) 
  # alldata$trawled.st <- arm::rescale(alldata$trawled) 
  # fit_formula <- paste0("treat ~ start_density.st + depth.st + trawled.st + muddy.st + any_rock.st") #+ + omega_s

  #fit <- McSpatial::matchprop(cell_type ~ start_density + depth, data= alldata, ytreat = "source")

@@

  # matched <- MatchIt::matchit(as.formula(fit_formula), data = alldata, method="nearest", discard="both")
  # mdata <- MatchIt::match.data(matched)

  # Uses logit matching for which most matches are higher that treatment values
  # mdata <- McSpatial::matchprop(as.formula(fit_formula), data = alldata, ytreat = 1, discard = "both", m.order = "decreasing")

  # Uses n mahalanobis distances
  mdata <- McSpatial::matchprop(as.formula(fit_formula), data = alldata, ytreat = 1, distance="probit", discard = "both", reestimate=TRUE) #m.order = "random", 
  #mdata <- McSpatial::matchmahal(as.formula(fit_formula), data = alldata, ytreat = 1, distance="mahal", discard = "both") #, reestimate=TRUE)
  #mdata <- McSpatial::matchmahal(as.formula(fit_formula), data = alldata, ytreat = 1, distance="probit", discard = "both") #, reestimate=TRUE) , m.order = "random"

  mdata <- mdata %>% rename(distance = vect_dist) #%>% select(-start_density.st, -depth.st, -muddy.st, -any_rock.st, -omega_s.st)

  matched_time0 <- mdata %>% mutate(after = 0, density = start_density) #%>% dplyr::select(-start_density, -end_density)
  matched_time1 <- mdata %>% mutate(after = 1, density = end_density) #%>% dplyr::select(-start_density, -end_density)

@@

Prep data
```{r}
data <- vocc_by_sp[["adult"]]
# View(data)

@@

Plot data
```{r}

ggplot(filter(data, as.numeric(matchobs) <= 150), aes(y=Y, x=X, shape=as.factor(treat), colour=matchobs)) +
  geom_point(alpha=0.4, size =4) +
  scale_shape_manual(values= c(4, 1)) +
  scale_colour_viridis_d(option="C", guide = FALSE)

lapply(variable_names, function(j) {
ggplot(data, aes(y=log_density, x=UQ(rlang::sym(paste(j))), colour=time)) +
  geom_point(alpha=0.35) +
  scale_colour_viridis_d(option="C") 
})

@@

ggplot(data, aes(log_density, fill = cell_type)) +
  geom_histogram(alpha=0.45) +
  scale_fill_viridis_d(option="C") +
  facet_wrap(~time)

@@

gam4 <- gamm4::gamm4(as.formula(gamm_formula), random = ~(1|matchobs) + (1|origobs), data=data) # + s(X,Y, bs="re")

# for (j in (variable_names)) {
#   gamm_formula <- paste0("log_density ~ time * cell_type + s(distance) + s(std_", j, ") + te(X,Y)")
# }
# gam <- mgcv::gamm(as.formula(gamm_formula), random = ~(1|matchobs) + (1|origobs), data=data) # + s(X,Y, bs="re")

@@

#my_cols <- c("#E69F00", "#56B4E9")
plot_parametric(igam4$gam, pred=list(time=c("begin","end"), cell_type=c("control", "source")), 
   parametricOnly = TRUE, main="", xlab ="log_density"
  #, groups = cell_type, gcolor = my_cols, color = my_cols["time"]
  ) 
```
